\Large \bf Uncovering Bugs in Distributed Storage Systems\\during Testing (not in Production!)

### 2015-09-22 paper.tex
updates
anonymization: azure -> mycloud, microsoft -> mycompany
update to include submission id and remove authors

@@

%for single author (just remove % characters)
\author{
{\rm Pantazis Deligiannis$^\dagger$, Matt McCutchen$^\diamond$, Paul Thomson$^\dagger$, Shuo Chen$^\star$}\\
{\rm Alastair F. Donaldson$^\dagger$, John Erickson$^\star$, Cheng Huang$^\star$, Akash Lal$^\star$}\\
{\rm Rashmi Mudduluru$^\star$, Shaz Qadeer$^\star$, Wolfram Schulte$^\star$}\\\\
$^\dagger$Imperial College London, $^\diamond$Massachusetts Institute of Technology, $^\star$Microsoft\\
} % end author

@@

Our methodology has been applied to three distributed storage systems in the Microsoft Azure cloud computing platform. In the process, numerous bugs were identified, reproduced, confirmed and fixed. These bugs required a subtle combination of concurrency and failures, making them extremely difficult to find with conventional testing techniques. An important advantage of our approach is that a bug is uncovered in a small setting and witnessed by a full system trace, which dramatically increases the productivity of debugging.

@@

\section{Testing Azure Storage vNext with \psharp}
\label{sec:method}

>>>>

\newcommand{\Azure}{MyCloud\xspace}
\newcommand{\Microsoft}{MyCompany\xspace}

@@

%for single author (just remove % characters)
\author{
{\rm Submission ID: \#127}} % end author
%\author{
%{\rm Pantazis Deligiannis$^\dagger$, Matt McCutchen$^\diamond$, Paul Thomson$^\dagger$, Shuo Chen$^\star$}\\
%{\rm Alastair F. Donaldson$^\dagger$, John Erickson$^\star$, Cheng Huang$^\star$, Akash Lal$^\star$}\\
%{\rm Rashmi Mudduluru$^\star$, Shaz Qadeer$^\star$, Wolfram Schulte$^\star$}\\\\
%$^\dagger$Imperial College London, $^\diamond$Massachusetts Institute of Technology, $^\star$Microsoft\\
%} % end author

@@

Our methodology has been applied to three distributed storage systems in the \Microsoft \Azure platform. In the process, numerous bugs were identified, reproduced, confirmed and fixed. These bugs required a subtle combination of concurrency and failures, making them extremely difficult to find with conventional testing techniques. An important advantage of our approach is that a bug is uncovered in a small setting and witnessed by a full system trace, which dramatically increases the productivity of debugging.

@@

\section{Testing \Azure Storage vNext with \psharp}
\label{sec:method}
